---
title: "Visualization"
subtitle: "Part I"
output: github_document
---

```{r setup}
library(tidyverse)
library(ggridges)
```

## Load the weather data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
        c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```



## Scatterplots

Create first scatterplot 

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point()
```

New approach, same plot

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```

Save and edit a plot object

```{r}
weather_plot = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax))

weather_plot + geom_point()
```

## Advanced scatterplot ...

Start with the same one and make it fancy

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() + 
  geom_smooth(se = FALSE)
```

What about the 'aes' placement?
  - ends up looking the same when 'aes' is in         geom_point line
  - add geom_smooth --> creates a single line         because geom_smooth only knows color as           applied to geom_point line 

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name)) +
  geom_smooth()
```

Facet some things
- plot that shows 3 locations by itself
- within each, scatter plot and smooth function 
- facet_grid "." says not to create rows ~ "names"     says to create columns with names 
- switch around - facet_grid(names ~ .)
    - creates rows not columns 
- could define all transparency (alpha) and size in terms of a variable (in the ggplot line)
    
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .2) + 
  geom_smooth(se = FALSE, size = 2) +
  facet_grid(. ~ name)
```


Combine elements, and try new plot 

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp ), alpha = .5) +
  geom_smooth(se = FALSE)+
  facet_grid(. ~ name)
```

## Some small notes

How many geoms have to exist?

  - you can have whatever geoms you want

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_smooth(se = FALSE)
```

You can use a neat geom

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex()
```

  - like hex but squares....

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_bin2d()
```

  - like a contour plot
  
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_density2d() +
  geom_point(alpha = .3)
```





